Self Regulation Ontology Retest Data Report

### 2017-04-14 SRO_Report.Rmd
begun ddm variable comparisons

```{r warning=FALSE, message=FALSE, eval=FALSE}
#Plot of distribution of icc's faceted by putative measure
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  separate(measure_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  gather(key, value, -dv, -icc, -spearman) %>%
  arrange(dv) %>%
  drop_na() %>%
  mutate(value = trim(value)) %>%
  filter(dv %in% c("dot_pattern_expectancy.bias", "go_nogo.bias") == FALSE)%>%
  ggplot(aes(icc))+
  geom_histogram(position = 'identity', alpha=0.5)+
  theme_bw()+
  facet_wrap(~value)
```

@@

>>>>

@@

- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
- Raw variables are not the variables with highest reliabilities overall.  
- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.
